\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Nathan Kramer} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+1(651) 895--2025 \\ Minneapolis, MN}
\address{\href{mailto:kramernate0@gmail.com}{kramernate0@gmail.com} \\ \href{https://www.linkedin.com/in/nathan-kramer-a71060161/}{linkedin} \\ \href{https://www.github.com/kramen22}{github.com/kramen22}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

{Software Engineer with 4+ years of experience in back-end development, seeking full-time back-end engineering roles.}


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{@{} >{\bfseries}l @{\hspace{6ex}} l }
Technical Skills & git, golang, terraform, java, javascript\\
Soft Skills & Remote work communication (Slack), Technical Writing, Technical Leadership\\
Platforms & AWS, Cloudflare, Github Actions, Datadog, Gitlab CI/CD, Jenkins\\
\end{tabular}\\
\end{rSection}

\begin{rSection}{EXPERIENCE}

\textbf{Engineer III} \hfill Jul 2021 -- Present\\
FloatMe \hfill \textit{San Antonio, TX (Remote)}
 \begin{itemize}
    \itemsep-3pt {}
     \item Implemented a new authentication reverse proxy to protect against password stuffing attacks deployed via cloudflare workers.
     \item Led the implementation of event driven microservices for user, subscription, and loan business resources.
    \item Created Datadog dashboards and added key logs and metrics to increase observability into payment processing and collection attempts in real time.
    \item Integrated with multiple third parties including Auth0 and Castle to create real time risk assesments of login attempts to reduce bot traffic of API endpoints.
    \item Mentored new engineers during onboarding as well as provided feedback and guidance for junior engineers to improve the quality of their code.
    \item Engineered parts of an SDK to help DRY up codebases and improve development velocity across teams.
 \end{itemize}

\textbf{Application Developer} \hfill Sep 2018 -- Jul 2021\\
Sprint/T-Mobile \hfill \textit{Dallas, TX}
 \begin{itemize}
    \itemsep-3pt {}
     \item Outlined and implemented the first RESTful service in the wireline service delivery department.
     \item Updated software projects to use Maven dependency management to keep software up to date and easier to build cross team.
 \end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{Payment Processing Observability.} {Worked with the business and BI teams to identify metrics and events to track to improve payment risk, as well as reduce NACHA errors that incur fines. Implemented fixes based on errors discovered to reduce cash burn from these fines.}
\item \textbf{golflog.} {Helped create and open source a golang logger that embeds itself in a context and can be easily configured with different levels to increase or reduce verbosity. Check it out here: \href{https://github.com/floatme-corp/golflog}{golflog}}
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor of Computer Science}, Iowa State University \hfill {2015 -- 2018}

\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Curricular Activities}
\begin{itemize}
    \item 	Volunteered as a project mentor for CodeDay which is a hackathon weekend for students, check it out at \href{https://www.codeday.org/}{codeday.org}
    \item Volunteered at Special Olympics Minnesota state and regional meets, volunteer or donate at \href{https://specialolympicsminnesota.org/}{specialolympicsminnesota.org}
\end{itemize}


\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}

